Structured Versus Decorated Cospans

### 2021-01-12 cospans.tex
various edits according to yesterday's meeting

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/8

@@

Building towards an isomorphism of the above described double categories, we now define a double functor sending structured cospans to decorated cospans:
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp.
\end{displaymath}
We set $\lE_0 \maps \A \to \A$ to be the identity, and decree that $\lE_1$ sends any
$L$-structured cospan as in \cref{eq:scsphor1cell} to the decorated cospan
$a \xrightarrow{i} m \xleftarrow{o} b$ with decoration $x\in F(m)$, whereas $\lE_1$ sends 
any map of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} to the
map of $F$-decorated cospans given by
\[
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\]
along with the morphism of decorations $\tau\maps F(k)(x) \to x'$ in $F(m')$ coming from the middle arrow of \cref{eq:2morphismLCspintaF}. We then make $\lE$ into double functor as in \cref{def:doublefun}. First, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.  Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$. Explicitly, $\mathbb{E}(N)\odot \mathbb{E}(M)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b\ar[ul]
 \end{tikzcd}\qquad
  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn).
\end{equation}
On the other hand, $N \odot M$ computed as in \cref{eq:globalpushout} is 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(v_m)x+_{(\bot_{m+_bn})}F(v_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $v_m,v_n$ are the canonical maps into the pushout.  Under $\lE$ this is mapped to the cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$ -- since a pushout over an initial object is just a sum.  This decoration is canonically isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{equation}\label{eq:isomorphismdiag}
 \begin{tikzcd}[sep=.4in]
F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\stackrel{\phi_{v_m,v_n}}{\cong}"] & F(m+n)\ar[r,"F(\psi)"]\ar[dr,phantom,"\cong"']\ar[d,"F(v_m+v_n)"] & F(m+_bn)\ar[d,"F(1)"]\\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{equation}
where the composite of the bottom two arrows is the coproduct $+ \maps F(m+_bn) \times F(m+_bn) \to F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand isomorphism comes from pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and pseudofunctoriality of $F$.  Thus, we have a globular 2-isomorphism  $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$. Notice that since the target decoration is part of the above pushout in the Grothendieck category $\inta F$, this isomorphism we construced is the canonical such that it commutes with the respective cocones. This is useful when checking associativity for example: there is only one such canonical isomorphism $\lE(P)\odot\lE(N)\odot\lE(M)\to\lE(P\odot N\odot M)$ for any three composable structured cospans.

Finally, we construct a globular 2-isomorphism $U_{\lE (m)} \simrightarrow\lE(U_m)$. The identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.

In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms. Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibers provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above. As a result, we have a double isomorphism 
\begin{equation}\label{eq:doubleiso}
_L\lCsp(\inta F) \cong F\lCsp.
\end{equation}

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')\in F(m+m')
%\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m')
\\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big) \\
&=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }F(\iota_m)x+F(\iota_{m'})x'\in F(m+m')
\end{align*}
The cospan part is equal, whereas we have an isomorphism between the decorations, $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$, given in an analogous way to \cref{eq:isomorphismdiag} as follows:
\begin{displaymath}
\begin{tikzcd}[sep=.4in]
F(m)\times F(m')\ar[r,"\phi_{m,m'}"]\ar[d,"F(\iota_m)\times F(\iota_{m'})"']
\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+m')\ar[dr,"F(1)"]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{m'})"']  & \\
F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"'] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
 \end{tikzcd}
\end{displaymath}
where the composite of the bottom two arrows is the coproduct operation in $F(m+m')$.
We thus have constructed an isomorphism $\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$. 
Again, notice that since the target decoration is part of the sum $\left(m+m',F(\iota_m)x+F(\iota_{m'})x'\right)$ in the Grothendieck category $\inta F$ by \cref{eq:fibrewisecoprod}, this isomorphism we constructured is the canonical such that it commutes with the respective inclusions into the sum, and there is only one such canonical isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans, proving associativity.

Moreover, the monoidal unit $I_1$ for ${}_L \lCsp(\inta F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor.

Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations involving universal property arguments. In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
\end{proof}

@@

\begin{defn}\label{defn:monoidal_double_functor}
Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with invertible transformations $\theta \maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \maps I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
\end{defn}
%{\chris Those units in the definition should be monoidal units not unit functors...}
%%% Kenny: How about I instead of 1?
%%% Christina: Sure but that was NOT in the definition of symmetric monoidal double category above...could you streamline??
\noindent
Explicitly, a symmetric monoidal double functor is a double functor $\lF \maps \lD \to \lE$ such that:
\begin{itemize}
\item{$\lF_0$ and $\lF_1$ are symmetric monoidal functors,}
\item{we have equalities $\lF_0 S_{\lD} = S_{\lE} \lF_1$ and $\lF_0 T_{\lD} = T_{\lE} \lF_1$ of monoidal functors, and}
\item{the following diagrams commute, expressing that $\phi$ is a transformation of double categories:
		\begin{equation}
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$ (\lF(M_2)\otimes \lF(N_2))\odot (\lF(M_1)\otimes \lF(N_1))$}};
			\node (A') at (0,0) {\footnotesize{$(\lF(M_2) \odot \lF(M_1)) \otimes (\lF(N_2) \odot \lF(N_1))$}};
			\node (B) at (5,1.5) {\footnotesize{$\lF(M_2 \otimes N_2)\odot \lF(M_1 \otimes N_1)$}};
			\node (B') at (5,0) {\footnotesize{$\lF((M_2 \otimes N_2)\odot(M_1 \otimes N_1))$}};
			\node (A'') at (0,-1.5) {\footnotesize{$\lF(M_2 \odot M_1) \otimes \lF(N_2 \odot N_1)$}};
			\node (B'') at (5,-1.5) {\footnotesize{$\lF((M_2 \odot M_1)\otimes(N_2 \odot N_1))$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\phi \odot \phi$} (B)
				(B) edge node[right]{$\lF_\odot$} (B')
				(A') edge node [left] {$\lF_\odot \otimes \lF_\odot$} (A'')
				(B') edge node [right] {$\lF(\chi)$} (B'')
				(A'') edge node[above]{$\phi$} (B'');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
			\node (A') at (0,0) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{\lF(a \otimes b)} $}};
			\node (B') at (2,0) {\footnotesize{$\lF(U_{a \otimes b})$}};
			\node (A'') at (0,-1.5) {\footnotesize{$\lF(U_a) \otimes \lF(U_b)$}};
			\node (B'') at (2,-1.5) {\footnotesize{$\lF(U_a \otimes U_b) $}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\mu$} (A')
				(A') edge node [left] {$\lF_\mu \otimes \lF_\mu$} (A'')
				(B') edge node [right] {$\lF \circ \mu$} (B'')
				(A) edge node[above]{$U_\phi$} (B)
				(B) edge node[right]{$\lF_U$} (B')
				(A'') edge node[above]{$\phi$} (B'');
		\end{tikzpicture}
		\end{equation}
}
\end{itemize}
\noindent

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/12

@@

Building towards an isomorphism of the above described double categories, we now define a double functor sending structured cospans to decorated cospans:
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp.
\end{displaymath}
We set $\lE_0 \maps \A \to \A$ to be the identity, and decree that $\lE_1$ sends any
$L$-structured cospan as in \cref{eq:scsphor1cell} to the decorated cospan
$a \xrightarrow{i} m \xleftarrow{o} b$ with decoration $x\in F(m)$, whereas $\lE_1$ sends 
any map of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} to the
map of $F$-decorated cospans given by
\[
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\]
along with the morphism of decorations $\tau\maps F(k)(x) \to x'$ in $F(m')$ coming from the middle arrow of \cref{eq:2morphismLCspintaF}. We then make $\lE$ into double functor as in \cref{def:doublefun}. First, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.  Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$. Explicitly, $\mathbb{E}(N)\odot \mathbb{E}(M)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b\ar[ul]
 \end{tikzcd}\qquad
  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn).
\end{equation}
On the other hand, $N \odot M$ computed as in \cref{eq:globalpushout} is 
\begin{equation}\label{eq:pushoutissum}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(v_m)x+_{(\bot_{m+_bn})}F(v_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{equation}
where $v_m,v_n$ are the canonical maps into the pushout.  Under $\lE$ this is mapped to the cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$ -- since a pushout over an initial object is just a sum.  This decoration is canonically isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{equation}\label{eq:isomorphismdiag}
 \begin{tikzcd}[sep=.4in]
F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\stackrel{\phi_{v_m,v_n}}{\cong}"] & F(m+n)\ar[r,"F(\psi)"]\ar[dr,phantom,"\cong"']\ar[d,"F(v_m+v_n)"] & F(m+_bn)\ar[d]\\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{equation}
where the composite of the bottom two arrows is the coproduct $+ \maps F(m+_bn) \times F(m+_bn) \to F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand isomorphism comes from pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and pseudofunctoriality of $F$.  Thus, we have a globular 2-isomorphism  $\lE_\odot\colon\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.

Finally, we construct a globular 2-isomorphism $U_{\lE (m)} \simrightarrow\lE(U_m)$. The identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}. It can be verified that with this structure, $\lE$ satisfies the axioms of a double functor.

In fact, this double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms. Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibers provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above. As a result, we have a double isomorphism 
\begin{equation}\label{eq:doubleiso}
_L\lCsp(\inta F) \cong F\lCsp.
\end{equation}

Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric monoidal double functor as per \cref{defn:monoidal_double_functor}. Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially. For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
\begin{align*}
\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')\in F(m+m')
%\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m')
\\
\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big) \\
&=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }F(\iota_m)x+F(\iota_{m'})x'\in F(m+m')
\end{align*}
The cospan part is equal, whereas we have an isomorphism between the decorations, $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$, given in an analogous way to \cref{eq:isomorphismdiag} as follows:
\begin{equation}\label{eq:Elaxator}
\begin{tikzcd}[sep=.4in]
F(m)\times F(m')\ar[r,"\phi_{m,m'}"]\ar[d,"F(\iota_m)\times F(\iota_{m'})"']
\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{\iota_m,\iota_{m'}}}{\cong}}"] & F(m+m')\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{m'})"']  & \\
F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"'] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
 \end{tikzcd}
\end{equation}
where the composite of the bottom two arrows is the coproduct operation in $F(m+m')$.
We thus have constructed an isomorphism $\lE_\otimes\colon\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$.

Moreover, the monoidal unit $I_1$ for ${}_L \lCsp(\inta F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor. For example, the associativity axiom ensuring that the two ways to go from $\lE (M)\ot\lE(M')\ot\lE(M'')$ to $\lE(M\ot M'\ot M'')$ using the above structure isomorphisms are equal, can in fact be deduced from the more general 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$ already discussed in \cite[Theorem 2.7]{Shulman2008}, for the induced global monoidal structure given by $(\phi,\phi_0)$ as discussed in \cref{lem:MonGroth}. Moreover, the earlier associativity axiom for the double functor structure isomorphism $\lE_\odot$ can be deduced using the one for $\lE_\otimes$, by observing that \cref{eq:isomorphismdiag} factors through \cref{eq:Elaxator} as follows
\begin{displaymath}
\begin{tikzcd}[column sep=.4in]
F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(\iota_m)\times F(\iota_{n})"']\ar[dd,bend right=80,out=-90,in=-90,"F(v_m)\times F(v_n)"',"\textstyle\cong"]
\ar[dr,phantom,"{\stackrel{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+n)\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{n})"']  & \\
F(m+n)\times F(m+n)\ar[d,"F(\psi)\times F(\psi)"']\ar[dr,phantom,"\stackrel{\phi_{\psi,\psi}}{\cong}"]\ar[r,"\phi_{m+n,m+n}"'] & F\left((m+n)+(m+n)\right)\ar[r,"F(\nabla)"']\ar[d,"F(\psi+\psi)"']\ar[dr,phantom,"\cong"] & F(m+n)\ar[d,"F(\psi)"] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F((m+_bn)+(m+_bn))\ar[r,"F(\nabla)"'] & F(m+_bn)
\end{tikzcd}
\end{displaymath}
due $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.

In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the involved structures. In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
\end{proof}

Notice that in the above proof, when we compose two structured cospans namely horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object. Consequently, one could remark that in fact, the assumptions of \cref{thm:equiv} should only state that the corresponding pseudofunctor $F\colon \A\to\SMC$ factors through categories with finite coproducts rather than $\Rex$. We leave the statement as is in order to match the general assumptions of \cref{thm:SC} for the definition of the structured cospan symmetric monoidal double category.

@@

\begin{defn}\label{defn:monoidal_double_functor}
Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with invertible transformations $\theta \maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \maps I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
\end{defn}
%{\chris Those units in the definition should be monoidal units not unit functors...}
%%% Kenny: How about I instead of 1?
%%% Christina: Sure but that was NOT in the definition of symmetric monoidal double category above...could you streamline??
\noindent
Explicitly, a symmetric monoidal double functor is a double functor $\lF \maps \lD \to \lE$ such that:
\begin{itemize}
\item{$\lF_0$ and $\lF_1$ are symmetric monoidal functors,}
\item{we have equalities $\lF_0 S_{\lD} = S_{\lE} \lF_1$ and $\lF_0 T_{\lD} = T_{\lE} \lF_1$ of monoidal functors, and}
\item{the following diagrams commute, expressing that $\phi$ is a transformation of double categories:
		\begin{equation}
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$ (\lF(M_2)\otimes \lF(N_2))\odot (\lF(M_1)\otimes \lF(N_1))$}};
			\node (A') at (0,0) {\footnotesize{$(\lF(M_2) \odot \lF(M_1)) \otimes (\lF(N_2) \odot \lF(N_1))$}};
			\node (B) at (5,1.5) {\footnotesize{$\lF(M_2 \otimes N_2)\odot \lF(M_1 \otimes N_1)$}};
			\node (B') at (5,0) {\footnotesize{$\lF((M_2 \otimes N_2)\odot(M_1 \otimes N_1))$}};
			\node (A'') at (0,-1.5) {\footnotesize{$\lF(M_2 \odot M_1) \otimes \lF(N_2 \odot N_1)$}};
			\node (B'') at (5,-1.5) {\footnotesize{$\lF((M_2 \odot M_1)\otimes(N_2 \odot N_1))$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\phi \odot \phi$} (B)
				(B) edge node[right]{$\lF_\odot$} (B')
				(A') edge node [left] {$\lF_\odot \otimes \lF_\odot$} (A'')
				(B') edge node [right] {$\lF(\chi)$} (B'')
				(A'') edge node[above]{$\phi$} (B'');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
			\node (A') at (0,0) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{\lF(a \otimes b)} $}};
			\node (B') at (2,0) {\footnotesize{$\lF(U_{a \otimes b})$}};
			\node (A'') at (0,-1.5) {\footnotesize{$\lF(U_a) \otimes \lF(U_b)$}};
			\node (B'') at (2,-1.5) {\footnotesize{$\lF(U_a \otimes U_b) $}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\mu$} (A')
				(A') edge node [left] {$\lF_\mu \otimes \lF_\mu$} (A'')
				(B') edge node [right] {$\lF \circ \mu$} (B'')
				(A) edge node[above]{$U_\phi$} (B)
				(B) edge node[right]{$\lF_U$} (B')
				(A'') edge node[above]{$\phi$} (B'');
		\end{tikzpicture}
		\end{equation}
}
\end{itemize}
\noindent
%%% Christina: the notation is not streamlined. We occasionally use $F_\otimes$ and $F_\odot$ (which I prefer) and in the definitions above we use various greek letters like $\phi$ (which is definitely overused in our paper). Could this be fixed throughout the document? Similarly for the unit comparison maps.
